### 2019-03-10 manuscript/results.tex
fixing supplementary info crefs

We considered models both with or without diploidization in order to explore the effects of this process on the estimates of state-dependent diversification.
For the two models that only include diploid and polyploid states (D/P and D/P+A/B), the net diversification rate of polyploid lineages is likely negative when diploidization (parameter $\delta$) is excluded but positive when $\delta$ is included (\cref{figure:netdivall}A versus \cref{figure:netdivnodip}A).
For the two models that also included breeding system (ID/CD/CP and ID/CD/CP+A/B), the main effect of including diploidization is increasing the uncertainty of the estimate of polyploid net diversification rate (\cref{figure:netdivall}EF versus \cref{figure:netdivnodip}CD).
For all models, there is greater uncertainty in the estimate of diploidization rate than polyploidization rate, as judged by the width of the credibility intervals (see supplementary information figures). % todo: precise figure refs here

>>>>

We considered models both with or without diploidization in order to explore the effects of this process on the estimates of state-dependent diversification.
For the two models that only include diploid and polyploid states (D/P and D/P+A/B), the net diversification rate of polyploid lineages is likely negative when diploidization (parameter $\delta$) is excluded but positive when $\delta$ is included (\cref{figure:netdivall}A versus \cref{figure:netdivnodip}A).
For the two models that also included breeding system (ID/CD/CP and ID/CD/CP+A/B), the main effect of including diploidization is increasing the uncertainty of the estimate of polyploid net diversification rate (\cref{figure:netdivall}EF versus \cref{figure:netdivnodip}CD).
For all models, there is greater uncertainty in the estimate of diploidization rate than polyploidization rate, as judged by the width of the credibility intervals (see \cref{suppfigure:DP,suppfigure:DPAB,suppfigure:IDCDCP,suppfigure:IDCDCPAB}).
